### 2015-05-22 rscripts/data_review.Rmd
sorting out the view of reference individuals

```{r, echo=FALSE}
reference.dt <- merge(censor.dt, censor.dt[,list(tot = (max(logout) - min(login))/(365*24*60*60)), by=user_id][tot > 1, list(user_id = user_id)], by="user_id")
setkeyv(reference.dt, key(censor.dt))
ref.dt <- reference.dt[,
  list(
    overnight_logins = sum(login_day != logout_day),
    non_overnight_logins = sum(login_day == logout_day),
    mean_session_min = mean(logout-login)/60,
    total_session_min = sum(logout-login)/60,
    user_lifetime_days = max(logout_day) - min(login_day)
), by=user_id][,total_logins := overnight_logins + non_overnight_logins]
hist(ref.dt$overnight_logins/c(ref.dt$overnight_logins + ref.dt$non_overnight_logins))
hist(ref.dt$mean_session_min)
fitting <- function(runs, p_continue) sum(rnbinom(n=runs, size=1, prob=1-p_continue))/runs
with(ref.dt, {
  plot(total_logins, mean_session_min)
  points(total_logins, sapply(total_logins, fitting, p_continue = 0.99), pch=".", col = "red")
})

plot()
```

>>>>

```{r, echo=FALSE}
reference.dt <- merge(censor.dt, censor.dt[,list(tot = (max(logout) - min(login))/(365*24*60*60)), by=user_id][tot > 1, list(user_id = user_id)], by="user_id")
setkeyv(reference.dt, key(censor.dt))
ref.dt <- reference.dt[,
  list(
    overnight_logins = sum(login_day != logout_day),
    non_overnight_logins = sum(login_day == logout_day),
    mean_session_min = mean(logout-login)/60,
    total_session_min = sum(logout-login)/60,
    user_lifetime_days = max(logout_day) - min(login_day)
), by=user_id][,total_logins := overnight_logins + non_overnight_logins]
setkey(ref.dt, total_logins)
```

```{r,echo=FALSE}
sess_scale_min <- log10(c(10, 60, 2*60, 24*60, 7*24*60, 30*24*60, 6*30*24*60, 365*24*60))
sess_labels <- c("10 min", "1 hr", "2 hr", "1 day", "1 week", "1 month", "6 months", "1 year")

use_period_scale_day <- log10((1:5)*365)
use_period_labels <- c(1,2,3,4,5)

ggplot(ref.dt) + theme_bw() + 
  aes(x=log10(user_lifetime_days), y=log10(total_session_min), color=log10(total_logins)) + 
  geom_point() +
  scale_y_continuous("Total Session Time", breaks=sess_scale_min, labels=sess_labels) +
  scale_x_continuous("Usage Period (Years)", breaks=use_period_scale_day, labels=use_period_labels) +
  scale_color_continuous("Unique Logins", breaks=log10(c(10,100,1000)), labels=c(10,100,1000))
```

```{r, echo=FALSE}
#with(ref.dt, {

#  hist(ref.dt$overnight_logins/c(ref.dt$overnight_logins + ref.dt$non_overnight_logins))
#hist(ref.dt$mean_session_min)
#fitting <- function(runs, p_continue) sum(rnbinom(n=runs, size=1, prob=1-p_continue))/runs

#  plot(user_lifetime_days, total_logins, pch=".", alpha=0.5)
#  plot(total_logins, mean_session_min)
#  points(total_logins, sapply(total_logins, fitting, p_continue = 0.99), pch=".", col = "red")
#})
```
